Computer Science House Constitution

### 2017-05-04 articles.tex
Specify 'Votes Collected' (#101)
Additional wording so intent of the Alternative Vote could be better understood.

\asubsection{Alternative}
The winning option is selected outright if it gains more than half the votes as a first preference.
If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
This process continues until one option has half of the votes and is elected.

>>>>

\asubsection{Alternative}
The winning option is selected outright if it gains more than half the votes collected as a first preference.
If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
This process continues until one option has half of the votes collected and is elected.
